---
title: "Analyzing Simulated Error Estimates"
author: "Jonathan Che"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
require(tidyverse)
require(knitr)
require(kable)
require(kableExtra)

# Discrete scales for color and linetype
cc <- scales::seq_gradient_pal("blue", "orange", "Lab")(seq(0,1,length.out=5))
cl <- c("solid", "longdash", "dashed", "dotted")
```

## Setup

```{r, include=FALSE}
sims_FF <- read_csv("Results/assessment/sim-spvars-FALSE_spnoise-FALSE_100x100-500_cv4x4-k16-buffer15_seed100_plusA_noFlip_decay10.csv")
sims_FT <- read_csv("Results/assessment/sim-spvars-FALSE_spnoise-TRUE_100x100-500_cv4x4-k16-buffer15_seed123_noisier.csv")
sims_TF <- read_csv("Results/assessment/sim-spvars-TRUE_spnoise-FALSE_100x100-500_cv4x4-k16-buffer15_seed123_noisier.csv")
sims_TT <- read_csv("Results/assessment/sim-spvars-TRUE_spnoise-TRUE_100x100-500_cv4x4-k16-buffer15_seed100_plusA_noFlip_decay10.csv")
```

```{r, echo=FALSE}
# Summary tables for means
sims_FF %>%
  gather(
    key=method, value=estimate, 
    err_true:err_sloo) %>%
  group_by(method) %>%
  summarize(avg_est = mean(estimate)) %>%
  arrange(factor(avg_est))

sims_FT %>%
  gather(
    key=method, value=estimate, 
    err_true:err_sloo) %>%
  group_by(method) %>%
  summarize(avg_est = mean(estimate)) %>%
  arrange(factor(avg_est))

sims_TF %>%
  gather(
    key=method, value=estimate, 
    err_true:err_sloo) %>%
  group_by(method) %>%
  summarize(avg_est = mean(estimate)) %>%
  arrange(factor(avg_est))

sims_TT %>%
  gather(
    key=method, value=estimate, 
    err_true:err_sloo) %>%
  group_by(method) %>%
  summarize(avg_est = mean(estimate)) %>%
  arrange(factor(avg_est))
```

Pretty output below

```{r, include=FALSE}
# Summary table for means
sims %>%
  rename(
    `Training Error` = err_train,
    `K-fold CV` = err_cv,
    `K-fold CV Flipped` = err_cv_flip,
    `Buffered Grid CV` = err_grid_buffer,
    `Buffered Grid CV Flipped` = err_grid_buffer_flip) %>%
  gather(
    `Assessment Method`, est_val, 
    `Training Error`:`Buffered Grid CV Flipped`) %>%
  group_by(`Assessment Method`) %>%
  summarize(`Average Error Estimate` = mean(est_val)) %>%
  arrange(factor(`Average Error Estimate`)) %>%
  kable(
    format = "latex", 
    digits = 3,
    booktabs = T)
```

```{r, echo=FALSE}
# Summary table for variances
sims_FF %>%
  gather(
    key=method, value=estimate, 
    err_true:err_sloo) %>%
  group_by(method) %>%
  summarize(est_var = var(estimate)) %>%
  arrange(factor(est_var))

sims_FT %>%
  gather(
    key=method, value=estimate, 
    err_true:err_sloo) %>%
  group_by(method) %>%
  summarize(est_var = var(estimate)) %>%
  arrange(factor(est_var))

sims_TF %>%
  gather(
    key=method, value=estimate, 
    err_true:err_sloo) %>%
  group_by(method) %>%
  summarize(est_var = var(estimate)) %>%
  arrange(factor(est_var))

sims_TT %>%
  gather(
    key=method, value=estimate, 
    err_true:err_sloo) %>%
  group_by(method) %>%
  summarize(est_var = var(estimate)) %>%
  arrange(factor(est_var))
```



Pretty table below

```{r}
# summary table for differences of means
sims %>%
  rename(
    `Training Error` = err_train,
    `K-fold CV` = err_cv,
    `K-fold CV Flipped` = err_cv_flip,
    `Buffered Grid CV` = err_grid_buffer,
    `Buffered Grid CV Flipped` = err_grid_buffer_flip) %>%
  gather(
    `Assessment Method`, est_val, 
    `Training Error`:`Buffered Grid CV Flipped`) %>%
  mutate(diff = abs(est_val-err_true)) %>%
  group_by(`Assessment Method`) %>%
  summarize(`Average Difference` = mean(diff)) %>%
  kable(
    format = "latex", 
    digits = 3,
    booktabs = T)
```




```{r}
# Density plots
sims_FF %>%
  gather(
    key=method, value=estimate, 
    err_train:err_sloo) %>%
  mutate(method = factor(method, levels=c("err_train", "err_cv", "err_cv_flip", "err_loo", "err_grid_buffer", "err_grid_buffer_flip", "err_sloo"))) %>%
  ggplot((aes(x=estimate-err_true))) +
  geom_density(aes(color=method, linetype=method)) +
  scale_linetype_manual(
    name="Error Estimation Method",
    values=c("solid", "solid", "dashed", "dotted", "solid", "dashed", "dotted")) +
  scale_color_manual(
    name="Error Estimation Method",
    values=c("blue", "black", "black", "black", "red", "red", "red")) +
  geom_vline(xintercept=0) +
  coord_cartesian(xlim=c(-0.1, 0.1)) +
  labs(
    y="Density",
    x="Error Estimate - True Error",
    color="Error Estimation Method"
  )

sims_FT %>%
  gather(
    key=method, value=estimate, 
    err_train:err_sloo) %>%
  mutate(method = factor(method, levels=c("err_train", "err_cv", "err_cv_flip", "err_loo", "err_grid_buffer", "err_grid_buffer_flip", "err_sloo"))) %>%
  ggplot((aes(x=estimate-err_true))) +
  geom_density(aes(color=method, linetype=method)) +
  scale_linetype_manual(
    name="Error Estimation Method",
    values=c("solid", "solid", "dashed", "dotted", "solid", "dashed", "dotted")) +
  scale_color_manual(
    name="Error Estimation Method",
    values=c("blue", "black", "black", "black", "red", "red", "red")) +
  geom_vline(xintercept=0) +
  coord_cartesian(xlim=c(-0.1, 0.1)) +
  labs(
    y="Density",
    x="Error Estimate - True Error",
    color="Error Estimation Method"
  )

sims_TF %>%
  gather(
    key=method, value=estimate, 
    err_train:err_sloo) %>%
  mutate(method = factor(method, levels=c("err_train", "err_cv", "err_cv_flip", "err_loo", "err_grid_buffer", "err_grid_buffer_flip", "err_sloo"))) %>%
  ggplot((aes(x=estimate-err_true))) +
  geom_density(aes(color=method, linetype=method)) +
  scale_linetype_manual(
    name="Error Estimation Method",
    values=c("solid", "solid", "dashed", "dotted", "solid", "dashed", "dotted")) +
  scale_color_manual(
    name="Error Estimation Method",
    values=c("blue", "black", "black", "black", "red", "red", "red")) +
  geom_vline(xintercept=0) +
  coord_cartesian(xlim=c(-0.1, 0.1)) +
  labs(
    y="Density",
    x="Error Estimate - True Error",
    color="Error Estimation Method"
  )

sims_TT %>%
  gather(
    key=method, value=estimate, 
    err_train:err_sloo) %>%
  mutate(method = factor(method, levels=c("err_train", "err_cv", "err_cv_flip", "err_loo", "err_grid_buffer", "err_grid_buffer_flip", "err_sloo"))) %>%
  ggplot((aes(x=estimate-err_true))) +
  geom_density(aes(color=method, linetype=method)) +
  scale_linetype_manual(
    name="Error Estimation Method",
    values=c("solid", "solid", "dashed", "dotted", "solid", "dashed", "dotted")) +
  scale_color_manual(
    name="Error Estimation Method",
    values=c("blue", "black", "black", "black", "red", "red", "red")) +
  geom_vline(xintercept=0) +
  coord_cartesian(xlim=c(-0.3, 0.1)) +
  labs(
    y="Density",
    x="Error Estimate - True Error",
    color="Error Estimation Method"
  )
```

Pretty graph below

```{r, include=FALSE}
# Density plot
sims %>%
  rename(
    `K-fold CV` = err_cv,
    `MPCV` = err_cv_flip,
    `Buffered Grid CV` = err_grid_buffer,
    `FBGCV` = err_grid_buffer_flip) %>%
  gather(
    err_est, est_val, 
    `K-fold CV`:`FBGCV`) %>%
  mutate(err_est = factor(err_est, levels=c("K-fold CV", "MPCV", "Buffered Grid CV", "FBGCV"))) %>%
  ggplot((aes(x=est_val-err_true))) +
  geom_density(aes(color=err_est, linetype=err_est)) +
  scale_linetype_manual(
    name="Error Estimation Method",
    values=c("solid", "dashed", "solid", "dashed")) +
  scale_color_manual(
    name="Error Estimation Method",
    values=c("black", "black", "red", "red")) +
  geom_vline(xintercept=0) +
  coord_cartesian(xlim=c(-0.5, 0.5)) +
  labs(
    y="Density",
    x="Error Estimate - True Error",
    color="Error Estimation Method"
  )
```

We note that flipped buffered grid CV both underpredicts and overpredicts model error with similar probabilities, which leads to greater average absolute error but an error distribution centered almost at the true error.

## Conclusion

Spatial CV methods are slightly more accurate at estimating model error!
